Using Genetic Algorithms to Optimize the Analogue Method for Precipitation forecasting in the Swiss Alps

### 2015-11-19 Optimization case study - Journal of Hydrology/template.tex
Simplification of the pressure levels tables.

\begin{equation}
\label{eq:S1}
S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
\end{equation}
where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points in the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation. The differences are processed separately in both directions. The smaller the S1 values are, the more similar the pressure fields.

@@

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the z4 method at the different subregions.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  & Z &   &   &   & Z &   &   & ZZ \\
			2  & Z &   &   &   & Z &   &   & ZZ \\
			3  & Z &   &   &   & Z &   &   & ZZ \\
			4  & Z &   &   &   & Z &   &   & ZZ \\
			5  &   &   & Z &   & Z &   &   & ZZ \\
			6  &   &   & Z &   & Z &   &   & ZZ \\
			7  &   &   & Z &   & Z &   &   & ZZ \\
			8  &   &   & Z &   & Z &   &   & ZZ \\
			9  &   &   & Z &   & Z &   &   & ZZ \\
			10 &   &   &   & Z & Z &   &   & ZZ \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4}
\end{table}

@@

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation of the z4-hi2 method, at the different subregions.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  & Z &   & Z &   &   & Z &   & Z \\
			2  & Z &   &   &   & Z & Z &   & Z \\
			3  & Z &   &   &   & Z & Z & Z &   \\
			4  &   &   & Z &   & Z & Z &   & Z \\
			5  &   & Z &   &   & Z &   & ZZ &   \\
			6  &   & Z &   &   & Z & Z &   & Z \\
			7  &   & Z &   &   & Z & Z &   & Z \\
			8  &   &   & Z &   & Z &   & ZZ &   \\
			9  &   & Z &   &   & Z & Z & Z &   \\
			10 &   & Z &   &   & Z & Z &   & Z \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi2}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of moisture of the z4-hi2 method, at the different subregions.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  &   &   &   &   & HH &   &   &   \\
			2  &   &   &   &   & HH &   &   &   \\
			3  &   &   &   &   & HH &   &   &   \\
			4  &   &   &   & H & H &   &   &   \\
			5  &   &   &   &   & HH &   &   &   \\
			6  &   &   &   & H & H &   &   &   \\
			7  &   &   &   & H & H &   &   &   \\
			8  &   &   &   & H & H &   &   &   \\
			9  &   &   &   & H & H &   &   &   \\
			10 &   &   &   & H & H &   &   &   \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi2_H}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation of the z4-hi4 method, at the different subregions.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  &   & Z & Z &   &   & Z &   & Z \\
			2  &   & Z &   &   & ZZ &   &   & Z \\
			3  &   & Z &   &   & Z & Z & Z &   \\
			4  &   &   & Z &   & Z & Z &   & Z \\
			5  &   & Z & Z &   &   & Z &   & Z \\
			6  &   & Z & Z &   &   & Z &   & Z \\
			7  &   & Z &   &   & ZZ &   &   & Z \\
			8  &   &   & Z & Z &   & Z &   & Z \\
			9  &   & Z &   &   & Z & Z & Z &   \\
			10 &   & Z & Z &   &   & ZZ &   &   \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi4}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of moisture of the z4-hi4 method,at the different subregions.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  &   &   & H &   & HH & H &   &   \\
			2  &   &   &   & H & HH & H &   &   \\
			3  &   &   &   & H & HHH &   &   &   \\
			4  &   &   &   & HH & HH &   &   &   \\
			5  &   &   &   & HH & HH &   &   &   \\
			6  &   &   &   & HH & H & H &   &   \\
			7  &   &   &   & HH & H & H &   &   \\
			8  &   &   &   & HH & H & H &   &   \\
			9  &   &   & H & H & H & H &   &   \\
			10 &   &   &   & H & HH & H &   &   \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi4_H}
\end{table}

@@

\begin{figure}[htb]
	\centerline{\includegraphics[width=7.9cm]{figures/figure_evolution.pdf}}
	\caption{Example of the best individuals evolution of 8 independent optimizations.}
	\label{fig:evolution}
\end{figure}

>>>>

\begin{equation}
\label{eq:S1}
S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
\end{equation}
where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points of the grid describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation. The differences are processed separately in both directions. The smaller the S1 values are, the more similar the pressure fields.

@@

\begin{table}[htbp]
	\footnotesize
	\caption{Pressure levels ($\sim$) automatically selected for the z4 method at the different subregions.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
			2  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
			3  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
			4  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
			5  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			6  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			7  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			8  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			9  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			10 &   &   &   & $\sim$ & $\sim$ &   &   & $\sim \sim$ \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4}
\end{table}

@@

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi2 method, at the different subregions.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  & $\sim$ &   & $\sim$ &   & $\bullet \bullet$  & $\sim$ &   & $\sim$ \\
			2  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
			3  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ & $\sim$ &   \\
			4  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
			5  &   & $\sim$ &   &   & $\sim \bullet \bullet$ &   & $\sim \sim$ &   \\
			6  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
			7  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
			8  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ &   & $\sim \sim$ &   \\
			9  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ & $\sim$ &   \\
			10 &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi2}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi4 method, at the different subregions.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  &   & $\sim$ & $\sim \bullet$ &   & $\bullet \bullet$ & $\sim \bullet$ &   & $\sim$ \\
			2  &   & $\sim$ &   & $\bullet$ & $\sim \sim \bullet \bullet$ & $\bullet$ &   & $\sim$ \\
			3  &   & $\sim$ &   & $\bullet$ & $\sim \bullet \bullet \bullet$ & $\sim$ & $\sim$ &   \\
			4  &   &   & $\sim$ & $\bullet \bullet$ & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
			5  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet \bullet$ & $\sim$ &   & $\sim$ \\
			6  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
			7  &   & $\sim$ &   & $\bullet \bullet$ & $\sim \sim \bullet$ & $\bullet$ &   & $\sim$ \\
			8  &   &   & $\sim$ & $\sim \bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
			9  &   & $\sim$ &  $\bullet$ & $\bullet$ & $\sim \bullet$ & $\sim \bullet$ & $\sim$ &   \\
			10 &   & $\sim$ & $\sim$ & $\bullet$ & $\bullet \bullet$ & $\sim \sim \bullet$ &   &   \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi4}
\end{table}

@@

\begin{figure}[htb]
	\centerline{\includegraphics[width=7.9cm]{figures/figure_evolution.pdf}}
	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
	\label{fig:evolution}
\end{figure}
